### 2014-10-28 Comprehensive/abstract.tex
Abstract rework.

\end{doublespace}
\newpage

>>>>

We propose to extend this research to include the ``gray box'' problem domain, which includes many
interesting real world problems. We plan to develop a variant of P3 which exploits
features of this domain, such as efficient local search and known variable linkage.
Furthermore, we want to examine how ``hamming ball search'' can be integrated into
global optimization, both through simple crossover and as part of P3.
Finally, we plan compare this P3 variant with state of the art black box, gray box, and
white box methods for solving challenging real world problems.
\end{doublespace}
\newpage
